FraCaS: Temporal Analysis

### 2020-11-09 paper2020/paper.tex
update formatting

\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}

\usepackage[hyperref]{naaclhlt2019}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{times}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage[capitalize]{cleveref}
\newlist{lingex}{enumerate}{3}
\setlist[lingex,1]{parsep=0pt,itemsep=1pt,label=(\arabic*),resume=lingexcount}
\newcommand\onelingex[1]{\begin{lingex}\item #1 \end{lingex}}

@@

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

%\newcommand\BibTeX{B{\sc ib}\TeX}

%\usepackage[backend=bibtex,citestyle=authoryear,style=authoryear,natbib]{biblatex}
% new style not compatible with biblatex
%\bibliography{../bbcl_lccm2018/bbcl_lccm2018.bib,iwcs2019}

\usepackage[verbose]{newunicodechar}
\input{../PaperTools/latex/newunicodedefs}

\title{FraCaS: Temporal Analysis}
\author{Jean-Philippe Bernardy \qquad Stergios Chatzikyriakidis \\
  University of Gothenburg\\
  {\tt firstname.lastname@gu.se} \\}

\date{}

\begin{document}
\maketitle

\begin{abstract}
  In this paper, we propose an implementation of temporal semantics
  which is suitable for inference problems. This implementation
  translates syntax trees to logical formulas, suitable for
  consumption by the Coq proof assistant. We support several phenomena
  including: temporal references, temporal adverbs, aspectual classes
  and progressives.  We apply these semantics to temporal problems of
  the FraCaS testsuite and obtain an accuracy of 81 percent.
\end{abstract}

@@

\ifanon
Anonymized
\else
The research reported in this paper was supported by grant 2014-39 from the
Swedish Research Council, which funds the Centre for Linguistic Theory and
Studies in Probability (CLASP) in the Department of Philosophy, Linguistics,
and Theory of Science at the University of Gothenburg. We are grateful to
our colleagues in CLASP for helpful discussion of some of the ideas presented
here. We also thank anonymous reviewers for their useful comments on an
earlier draft of the paper.
\fi
\bibliographystyle{acl_natbib}

>>>>

\documentclass[a4paper,twoside]{article}

\usepackage{subcaption}
% \usepackage{calc}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{times}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{url}
\usepackage[capitalize]{cleveref}
\usepackage[verbose]{newunicodechar}
\input{../PaperTools/latex/newunicodedefs}
\usepackage{SCITEPRESS}     % Please add other packages that you may need BEFORE the SCITEPRESS.sty package.

\newlist{lingex}{enumerate}{3}
\setlist[lingex,1]{parsep=0pt,itemsep=1pt,label=(\arabic*),resume=lingexcount}
\newcommand\onelingex[1]{\begin{lingex}\item #1 \end{lingex}}

@@

\begin{document}

\title{FraCaS: Temporal Analysis}
\author{\authorname{Jean-Philippe Bernardy} \authorname{Stergios Chatzikyriakidis}
  \affiliation{University of Gothenburg}
  \email{firstname.lastname@gu.se}}

\keywords{Temporal Semantics, Type-Theory}

\abstract{In this paper, we propose an implementation of temporal semantics
  which is suitable for inference problems. This implementation
  translates syntax trees to logical formulas, suitable for
  consumption by the Coq proof assistant. We support several phenomena
  including: temporal references, temporal adverbs, aspectual classes
  and progressives.  We apply these semantics to temporal problems of
  the FraCaS testsuite and obtain an accuracy of 81 percent.
}

\onecolumn \maketitle \normalsize \setcounter{footnote}{0} \vfill

@@

\ifanon
Anonymized
\else
The research reported in this paper was supported by grant 2014-39 from the
Swedish Research Council, which funds the Centre for Linguistic Theory and
Studies in Probability (CLASP) in the Department of Philosophy, Linguistics,
and Theory of Science at the University of Gothenburg. We are grateful to
our colleagues in CLASP for helpful discussion of some of the ideas presented
here. We also thank anonymous reviewers for their useful comments on an
earlier draft of the paper.
\fi
\bibliographystyle{apalike}
